Transferability of clinical prediction models for early trauma care

### 2019-09-10 ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd

---
title: "Transferability of clinical prediction models for early trauma care"
author: 
- Martin Henriksson
- Dell D Saulnier
- Johanna Berg
- Martin Gerdin Wärnberg
date: "September 09, 2019"
documentclass: "article"
output:
  word_document:
    reference_docx: transferstyle.docx
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

@@

In a clinical context, this suggests that clinical prediction models for early 
trauma care should be developed in settings with a high number of trauma patients.
These models could then be transferred to settings with less trauma patients, which 
should then result in a decreased mistriage rate in those settings.

In 2018, Granström et al. found that using a criteria-based triage system based on a 
clinical prediction model was effective in reducing overtriage without increasing 
mortality [@RN44]. Therefore, improving clinical prediction models to reduce mistriage is
clinically beneficial, potentially saving lives by minimizing undertriage, and likely 
saving resources by minimizing overtriage. Possibly, with registries as SweTrau, the analysis of 
model transfer could be performed continuously to optimize the models currently in use 
and advise which model transfers might be detrimental (or potentially beneficial).

>>>>

---
title: "Transferability of clinical prediction models for early trauma care"
author: 
- Martin Henriksson
- Dell D Saulnier
- Johanna Berg
- Martin Gerdin Wärnberg
date: "September 10, 2019"
documentclass: "article"
output:
  word_document:
    reference_docx: transferstyle.docx
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

@@

In a clinical context, this suggests that clinical prediction models for early 
trauma care should be developed in settings with a high number of trauma patients.
These models could then be transferred to settings with less trauma patients, which 
should then result in a decreased mistriage rate in those settings. In 2018, Granström 
et al. found that using a criteria-based triage system (i.e. a clinical prediction model) 
for trauma triage was effective in reducing overtriage without increasing mortality [@RN44]. 
Therefore, improving clinical prediction models to reduce mistriage is clinically beneficial, 
potentially saving lives by minimizing undertriage, and likely saving resources by 
minimizing overtriage. Possibly, with registries as SweTrau, the analysis of model 
transfer could be performed continuously to optimize the models currently in use and 
advise which model transfers might be detrimental (or potentially beneficial).
